SOMETHING ABOUT THE DISTRIBUTED AVERAGING BASED APPROXIMATION IN SENSOR NETWORKS

### 2022-10-18 paper.tex
version for Toon,Randy

    \item[(1)] A fully connected network, where node \(i\) communicates \(\|\bar{\h}_i\|\) to all other nodes \(\{j \in \Nset_i = \Mset \setminus i\}\) directly, i.e., the neighborhood is the full network.

@@

    \item[(3)] The node \(i\) communicates \(\|\bar{\h}_i\|\) only to neighboring nodes \(\{j \in \Nset_i \subset \Mset \setminus i\}\) and applies \(K\) distributed averaging iterations.

@@

For (1) and (2), the cost per node increases linearly with network size \(M\), whereas for communication scheme (3), the cost is linearly dependent on neighborhood size \(N_i\) and iteration count \(K\) only.

>>>>

    \item[(1)] A fully connected network, where node \(i\) communicates \(\|\bar{\h}_i\|\) to all other nodes \(\{j \in \Nset_i = \Mset\}\) directly, i.e., the neighborhood is the full network.

@@

    \item[(3)] The node \(i\) communicates \(\|\bar{\h}_i\|\) only to neighboring nodes \(\{j \in \Nset_i \subset \Mset\}\) and applies \(K\) distributed averaging iterations.

@@

For (1) and (2), the cost per node increases linearly with network size \(M\), whereas for communication scheme (3), the cost is linearly dependent on neighborhood size \(N_i\) and iteration count \(K\) only and therefore independent of network size.
